Brief notes on erosion

### 2017-07-18 docs/TexNotes/Notes.tex
Added ztest_channel.jl which just computes the flow in a 2D channel with no erodible bodies inside. This is useful to test my resistivity / permeability routines and I expect it could be useful for many other things in the future
Finished routines for resistivity

\section{Permeability, conductivity, drag, resistance, and all of that}

Darcy's law is
\begin{equation}
\bq = - \bvec{K} \grad \phi
\end{equation}
where $\bq$ is the specific discharge, $\phi = z + p/\gamma$ is the hydraulic head, and $\gamma = \rho g$. The rank-2 tensor $\bvec{K}$ is the {\em conductivity}, which is related to the {\em permeability} $\bvec{k}$ via $\bvec{K} = \bvec{k} \gamma/\mu$, where $\mu$ is the viscosity of the fluid. The units of conductivity are length-per-time (i.e.~velocity) and the units of permeability are length squared.
Perhaps the most standard parameter to characterize the porous medium is the permeability, so lets focus on that. Let us also eliminate gravity from consideration to get
\begin{equation}
\bq = - \bvec{k} \grad p / \mu
\end{equation}
Consider first an isotropic medium with permeability $k$ (scalar). I propose that we decompose the permeability into the contribution from channel walls and from the embedded bodies $k = k_{c} + k_{b}$. Lets first figure out the contribution from the channel walls $k_c$. Consider flow in a channel of width $2w$ due to a pressure difference of $\Delta p$ occurring over a length $2 \ell$, so that the pressure gradient is $\grad p = -\Delta p/(2 \ell)$. If I did it correctly, the velocity is
\begin{equation}
u(z) = \frac{\Delta p}{4 \mu \ell} (w^2 - z^2)
\end{equation}
Then we can calculate the discharge as
\begin{equation}
q = \frac{1}{2w} \int_{-w}^{w} u(z) dz = \frac{\Delta p w^2}{6 \mu \ell} = - \frac{w^2}{3 \mu} \grad p
\end{equation}
so that the channel permeability is given by
\begin{equation}
k_c = w^2/3
\end{equation}
This result at least has the correct units (length squared).

>>>>

\section{Permeability, conductivity, drag, resistance, and all that}

Darcy's law is
\begin{equation}
\bq = - \bvec{K} \grad \phi
\end{equation}
where $\bq$ is the specific discharge, $\phi = z + p/\gamma$ is the hydraulic head, and $\gamma = \rho g$. The rank-2 tensor $\bvec{K}$ is the {\em conductivity}, which is related to the {\em permeability} $\bvec{k}$ via $\bvec{K} = \bvec{k} \gamma/\mu$, where $\mu$ is the viscosity of the fluid. The units of conductivity are length-per-time (i.e.~velocity) and the units of permeability are length squared.
Perhaps the most standard parameter to characterize the porous medium is the permeability, so lets focus on that. Let us also eliminate gravity from consideration to get
\begin{equation}
\bq = - \bvec{k} \grad p / \mu
\end{equation}
Consider first an isotropic medium with permeability $k$ (scalar). Overall, it is more straightforward to work with the resistivity $r = 1/k$.

As a warmup, consider flow in a channel of width $2w$ due to uniform (negative) pressure gradient $p_x$ in the $x$-direction. The resulting velocity profile is
\begin{equation}
u(z) = -\frac{p_x}{2 \mu} (w^2 - z^2)
\end{equation}
Then we can calculate the discharge as
\begin{equation}
q = \frac{1}{2w} \int_{-w}^{w} u(z) dz = - \frac{ p_x w^2}{3 \mu} 
\end{equation}
so that the permeability due to the channel walls is $k_w = w^2/3$ and the resistivity is $r_w = 3/w^2$.

Next, consider the flow through a porous matrix (and set $\mu=1$ via nondimensionalization). Measure the pressure and velocity along two vertical lines, one at $x = x_0$ and another at $x = -x_0$, and average to get $p^+ = \left< p(x_0) \right>$, $p^- = \left<p(-x_0) \right>$ and the same for $q$. Then the {\em total} resistivity (that of the porous matrix and the channel walls together) is 
\begin{equation}
r_{tot} = \frac{p^- - p^+}{2 x_0 q_{avg}}
\end{equation}
This total resistivity reflects the resistivity from the porous matrix as well as the channel walls. There is a buffer region that lies outside the porous-matrix region ($x_0$ lies in the bugger region), and we would like to remove the contribution from this region. Lets regard the total resistivity as an area-integral of resistivity-density, so that we can write the total in terms of the areas of the regions
\begin{equation}
A_{t} r_{t} = A_{b} r_{b} + A_{m} r_{m}
\end{equation}
Here, the subscripts are as follows: $t$ stands for total, $b$ for buffer, and $m$ for matrix. Then we can solve for the resistivity in the matrix region
\begin{equation}
r_m = \frac{A_t r_t - A_b r_b}{A_m}
\end{equation}
In the buffer region, resistivity is only due to channel walls so that $r_b = 3$. The area of the included buffer region depends on $x_0$ via $A_b = 4(x_0 - 1)$. The area of the matrix region is always $A_m = 4$, and $A_t = A_b + A_m$. The resulting resistivity in the matrix, $r_m$, includes the contribution from the bodies as well as the channel walls. We can then subtract the contribution from the walls, to get $\tilde{r}_m$, the resistivity due to the bodies alone as
\begin{equation}
\tilde{r}_m = r_m - 3 \, .
\end{equation}
Putting everything together, the final formula is
\begin{equation}
\tilde{r}_m = x_0 (r_t - 3) \, .
\end{equation}
As convoluted as this calculation seems, it does appear to give convergent numerical results that are {\em independent of the choice of $x_0$} (to the expected order of accuracy).
